---
title: "graphic_description"
description: |
  I will create and describe one chart.
author:
  - name: Deschuyteneer Audry
    url: {}
date: 11-17-2020
output:
  distill::distill_article:
    self_contained: false
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
SciViews::R
```

```{r Importation, include=FALSE}
data <- read("urchin_bio", package = "data.io")
```

## Description du graphique.

I am going to analyze a chart that contains the size data of male urchins compare to female urchins. The goal is to compare the two sex of urchins to see which are the most profitable for food.


```{r Chart}
chart(data = urchin_bio, height ~ weight %col=% sex) +
   geom_point(na.rm = TRUE)
```
We notice that sex has little influence on the mass of urchins. This is beneficial because when fishing or rearing we cannot choose which urchin sex we are fishing. So my conclusion is that you don't have to breed a certain urchin sex to be profitable. Any urchin will have the same profitability as long as it is fished in the same environment.


Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

